Parsing Tweets into Universal Dependencies

### 2018-04-16 paper.tex
copyedits

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
(840 unique tweets, 639/201 for training/test), along with an 
additional 210 tweets sampled from the POS-tagged dataset of
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled
from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
The latter data source consists of 147.4M English tweets after being
filtered by the {\it lang} attribute in the tweet JSON and {\it
  langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}
In the same way as \citet{kong-EtAl:2014:EMNLP2014},
reference unit is always the tweet in its entirety
-- which may thus consist of multiple sentences -- not the sentence alone.%\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
Before annotation, we use a simple regular expression to anonymize usernames and URLs.

@@

Social media applications typically require processing large volumes
of data, making speed an important consideration. We therefore 
begin with the neural greedy stack LSTM parser introduced by \cite{ballesteros-dyer-smith:2015:EMNLP},
which can parse a sentence in linear time and harnesses 
character representations to construct word vectors, which should help mitigate the challenge of
spelling variation. We encourage the reader to refer their paper for
more details about the model.

@@

\paragraph{Learning from exploration.} When we set $\alpha =1$, we
eliminate the oracle from the estimation procedure (for the distilled
model).  This presents an opportunity to learn with \emph{exploration}, by
randomly sampling transitions from the ensemble, found useful
in recent methods for training greedy models that use dynamic oracles
\citep{goldberg-nivre:2012:PAPERS,TACL145,TACL885,ballesteros-EtAl:2016:EMNLP2016}.  
We find that this
approach outperforms the  conventional distillation model, coming in
1.5 point behind the ensemble (last line of Table~\ref{tbl:parse-result}).

>>>>

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
(840 unique tweets, 639/201 for training/test), along with an 
additional 210 tweets sampled from the POS-tagged dataset of
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled
from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
The latter data source consists of 147.4M English tweets after being
filtered by the {\it lang} attribute in the tweet JSON and {\it
  langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}
In the same way as \citet{kong-EtAl:2014:EMNLP2014},
reference unit is always the tweet in its entirety
-- which may thus consist of multiple sentences -- not the sentence alone. %\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
Before annotation, we use a simple regular expression to anonymize usernames and URLs.

@@

Social media applications typically require processing large volumes
of data, making speed an important consideration. We therefore 
begin with the neural greedy stack LSTM parser introduced by \citet{ballesteros-dyer-smith:2015:EMNLP},
which can parse a sentence in linear time and harnesses 
character representations to construct word vectors, which should help mitigate the challenge of
spelling variation. We encourage the reader to refer their paper for
more details about the model.

@@

\paragraph{Learning from exploration.} When we set $\alpha =1$, we
eliminate the oracle from the estimation procedure (for the distilled
model).  This presents an opportunity to learn with \emph{exploration}, by
randomly sampling transitions from the ensemble, found useful
in recent methods for training greedy models that use dynamic oracles
\citep{goldberg-nivre:2012:PAPERS,TACL145,TACL885,ballesteros-EtAl:2016:EMNLP2016}.  
We find that this
approach outperforms the  conventional distillation model, coming in
1.5 points behind the ensemble (last line of Table~\ref{tbl:parse-result}).
